\textbf{Seasonal Dynamics of Epiphytic Microbial Communities on Marine Macrophyte Surfaces}

### 2021-08-10 submission/manuscript.tex

DNA from surfaces of \emph{C. nodosa} and \emph{C. cylindracea} was
isolated from a pool of leaves or thalli on the sampling day using a
previously modified and adapted protocol that allows for a selective
epiphytic DNA isolation (Massana et al., 1997; Korlević et al., 2021).
Briefly, leaves and thalli were incubated in a lysis buffer and treated
with lysozyme and proteinase K. Following the incubations, the mixture
containing lysed epiphytic cells was separated from the leaves and
thalli and extracted using phenol-chloroform. Finally, the extracted DNA
was precipitated using isopropanol. DNA from seawater picoplankton was
extracted from 0.2 \si{\um} polycarbonate filters according to Massana
et al. (1997) with a slight modification. Following the
phenol-chloroform extraction, 1/10 of 3 \si{\Molar} sodium acetate (pH
5.2) was added. DNA was precipitated by adding 1 volume of chilled
isopropanol, incubating the mixtures overnight at \num{-20}
\si{\degreeCelsius} and centrifuging at 20,000 × \emph{g} and 4
\si{\degreeCelsius} for 20 \si{\minute}. The pellet was washed twice
with 500 \si{\ul} of chilled 70 \si{\percent} ethanol and centrifuged
after each washing step at 20,000 × \emph{g} and 4 \si{\degreeCelsius}
for 5 \si{\minute}. Dried pellets were re-suspended in 50 -- 100
\si{\ul} of deionized water.

>>>>

DNA from surfaces of \emph{C. nodosa} and \emph{C. cylindracea} was
isolated from a pool of leaves (1 g wet weight) or thalli (2 g wet
weight) on the sampling day using a previously modified and adapted
protocol that allows for a selective epiphytic DNA isolation (Massana et
al., 1997; Korlević et al., 2021). Briefly, leaves and thalli were
incubated in a lysis buffer and treated with lysozyme and proteinase K.
Following the incubations, the mixture containing lysed epiphytic cells
was separated from the leaves and thalli and extracted using
phenol-chloroform. Finally, the extracted DNA was precipitated using
isopropanol. DNA from seawater picoplankton was extracted from 0.2
\si{\um} polycarbonate filters according to Massana et al. (1997) with a
slight modification. Following the phenol-chloroform extraction, 1/10 of
3 \si{\Molar} sodium acetate (pH 5.2) was added. DNA was precipitated by
adding 1 volume of chilled isopropanol, incubating the mixtures
overnight at \num{-20} \si{\degreeCelsius} and centrifuging at 20,000 ×
\emph{g} and 4 \si{\degreeCelsius} for 20 \si{\minute}. The pellet was
washed twice with 500 \si{\ul} of chilled 70 \si{\percent} ethanol and
centrifuged after each washing step at 20,000 × \emph{g} and 4
\si{\degreeCelsius} for 5 \si{\minute}. Dried pellets were re-suspended
in 50 -- 100 \si{\ul} of deionized water. One DNA sample originating
from seawater picoplankton was obtained per each sampling point.
